Plots for Latent Hawkes Paper

### 2020-07-15 output_scripts/Paper_Plots.Rmd
update so can cache more easily

```{r process data for plot 10b}
current_cohort <- 1
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
sub.types <- c("All", "Active", "Inactive"); # three methods
task.types <- paste0("day", 1:21);

>>>>

```{r process data for plot 10b}
library(PlayerRatings)
current_cohort <- 1
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
sub.types <- c("All", "Active", "Inactive"); # three methods
task.types <- paste0("day", 1:21);
